Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-05-30 paper.tex
Blurb about how lessons learned may still be useful to future work (ref #14)
Include chart for frame rates from gnuplot
Added chart of frame rates using PGFPlots

\documentclass{article}
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{fancyvrb}

@@

@@

>>>>

\documentclass{article}
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{fancyvrb}
\usepackage{pgfplots}

@@

\begin{figure}
\centering
\includegraphics{frame-rates.pdf}
\label{frame-rates}
\end{figure}

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    xlabel=Samples,
    ylabel=Frames Per Second]
\addplot coordinates {
  (100, 22)
  (200, 10)
  (300, 7)
  (400, 5)
  (500, 4)
};
\addlegendentry{Slicing (attributes)}
\addplot coordinates {
  (100, 20)
  (200, 10)
  (300, 7)
  (400, 5)
  (500, 4)
};
\addlegendentry{Boolean XOR}
\addplot coordinates {
  (100, 20)
  (200, 10)
  (300, 6)
  (400, 4)
  (500, 4)
};
\addlegendentry{Depth-masking}
\addplot coordinates {
  (100, 6)
  (200, 3)
  (300, 2)
  (400, 1)
  (500, 1)
};
\addlegendentry{Slicing (uniforms)}
\end{axis}
\end{tikzpicture}
\caption{
Chart showing performance measurements as number of samples varies.  The slicing
with attributes, boolean XOR, and depth-masking methods are all about the same,
while the slicing with uniforms method lags behind considerably.
}
\end{figure}

@@

However, it is hoped that the lessons learned in this paper, namely that the
overhead incurred by multi-pass algorithms may outweigh the cost of streaming
geometry in other algorithms, will prove valuable to future endeavors in both
volume rendering and graphics in general.
